Meta-analysis

### 2019-07-26 05_MetaAnalysis.Rmd
Corrections made to raw data file updated the imputation of yield_error for trials lacking error

```{r Meta_dataImport}
PM_MB_means <- read.csv("data/1902 powdery mildew-Mungbean - Collated means.csv", stringsAsFactors = FALSE)

library(dplyr)
#str(PM_MB_means)
```

@@

```{r variance}
PM_MB_means %>%
   filter(Fungicide == "Tebeconazole",
          row_spacing == 0.75) %>%
   group_by(Y_error.type) %>%
   summarise(n = length(Y_error.type))

@@

plot(PM_MB_train$Yield_error, log(as.numeric(PM_MB_train$`grain_yield.t.ha.`)))

@@

PM_MB_trianLMER <- lmer(log(as.numeric(`grain_yield.t.ha.`)) ~ Yield_error + 
         (1|Trial_ref), data = PM_MB_train)

paramA <- (summary(PM_MB_trianLMER)$coef)[2,1]
InterC <- (summary(PM_MB_trianLMER)$coef)[1,1]

ggplot(PM_MB_train, aes(y = log(as.numeric(`grain_yield.t.ha.`)), x = Yield_error, colour = Trial_ref))+
   geom_point()+
   geom_abline(intercept = InterC, slope = paramA)

exp((log(as.numeric(PM_MB_means[PM_MB_means$Trial_ref == "mung1516/03",]$`grain_yield.t.ha.`)) * paramA)+InterC)
# PM_MB_means[PM_MB_means$Trial_ref == "mung1516/03",]$Yield_error
hist(PM_MB_train$Yield_error)
hist(as.numeric(PM_MB_train$`grain_yield.t.ha.`))
hist(log(as.numeric(PM_MB_means[PM_MB_means$Trial_ref == "mung1516/03",]$`grain_yield.t.ha.`)))

@@

>>>>

```{r Meta_dataImport}
PM_MB_means <- read.csv("data/1902 powdery mildew-Mungbean - Collated means.csv", stringsAsFactors = FALSE)
PM_MB_means$grain_yield.t.ha. <- as.numeric(PM_MB_means$grain_yield.t.ha.)
library(dplyr)
#str(PM_MB_means)
```

@@

```{r variance}
   PM_MB_means %>%
   filter(Fungicide == "Tebeconazole",
          row_spacing == 0.75) %>%
   group_by(Trial_ref, Y_error.type) %>%
   summarise(Tebe_Treatments = length(Y_error.type))
```

@@

plot(PM_MB_train$Yield_error, log(PM_MB_train$`grain_yield.t.ha.`))

@@

# Run a linear model with Yield error as a fixed effect predictor and Trial as a random intercept
PM_MB_trianLMER <- lmer(log(`grain_yield.t.ha.`) ~ Yield_error + 
         (1|Trial_ref), data = PM_MB_train)

paramA <- (summary(PM_MB_trianLMER)$coef)[2,1] # Extract the Slope to predict Yield error
InterC <- (summary(PM_MB_trianLMER)$coef)[1,1] # Extract the intercept to predict Yield error

lmer.coef <- coef(PM_MB_trianLMER)

# plot of the mixed effect model, Black line shows the mean lmer regression line
ggplot(PM_MB_train)+
   geom_point(aes(y = log(`grain_yield.t.ha.`), x = Yield_error, colour = Trial_ref))+
   geom_abline(intercept = c(InterC,lmer.coef$Trial_ref[,1]), 
               slope = c(paramA,lmer.coef$Trial_ref[,2]),
               size = 1.5,
               colour = c("Black",hue_pal()(6)))
   geom_point(aes(y = log(PM_MB_means[PM_MB_means$Trial_ref == "mung1516/03",]$`grain_yield.t.ha.`),
                  x = rep(0,length(log(PM_MB_means[PM_MB_means$Trial_ref == "mung1516/03",]$`grain_yield.t.ha.`)))
                  ),colour = "Black")

library(scales)

Sv <- (log(PM_MB_means[PM_MB_means$Trial_ref == "mung1516/03",]$`grain_yield.t.ha.`) - InterC)/ paramA

# PM_MB_means[PM_MB_means$Trial_ref == "mung1516/03",]$Yield_error
hist(PM_MB_train$Yield_error)
hist(PM_MB_train$`grain_yield.t.ha.`)
hist(log(as.numeric(PM_MB_means[PM_MB_means$Trial_ref == "mung1516/03",]$`grain_yield.t.ha.`)))

PM_MB_means[PM_MB_means$Trial_ref == "mung1516/03",]$Yield_error <- Sv
PM_MB_means[PM_MB_means$Trial_ref == "mung1516/03",]$Y_error.type <- "SamplingVariance"

@@

Just for kicks lets look at the linear regression model as a Random effects model where `Yield_error` is set as a random slope to the random intercept `Trial_ref`.  
The model fits better as shown by an anova comparison. But now to determine how to impute from this model ....
```{r random_slope_model}

# Run a linear model with Yield error as a fixed effect predictor and Trial as a random intercept
PM_MB_trianLMERx <- lmer(log(`grain_yield.t.ha.`) ~ 1 + 
         (Yield_error|Trial_ref), data = PM_MB_train)

anova(PM_MB_trianLMER,PM_MB_trianLMERx) # random slope model signigicantly better

summary(PM_MB_trianLMERx)

InterC <- (summary(PM_MB_trianLMER)$coef)[1,1] # Extract the intercept to predict Yield error

lmer.coef <- coef(PM_MB_trianLMERx)

# plot of the mixed effect model, Black line shows the mean lmer regression line
ggplot(PM_MB_train)+
   geom_point(aes(y = log(`grain_yield.t.ha.`), x = Yield_error, colour = Trial_ref))+
   geom_abline(intercept = lmer.coef$Trial_ref[,2], 
               slope = lmer.coef$Trial_ref[,1],
               size = 1.5,
               colour = hue_pal()(6))
